The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2016-01-13 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev1.tex
change to use nithyas simulations

\begin{figure*}[h]
\centering
\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_manyLSTs.pdf}
\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST2deg.pdf}
\includegraphics[width=6in]{delay_spectra_dave_rich_airy_beams_LST62deg.pdf}
\caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel). We plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models. The maximum horizon brightening at the negative horizon occurs at 2$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon. In contrast, when the horizon brightening effect is smaller at 2$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
\label{fig:delayspec}
\end{figure*}

@@

How much do the predicted foreground power spectra differ between the three model dish power patterns? Figure \ref{fig:delayspec} (middle panel) shows the simulated delay spectra for all three beams at $2^\circ$ LST, when the horizon brightening is worst. All three delay spectra agree out to delays of 10--20\,ns on the 14\,m baseline and 30--40\,ns on the 40\,m baseline. These numbers suggest that the beams track each other fairly well out to 15--20$^\circ$ from zenith, beyond which they diverge. This is roughly what is observed in Figure \ref{fig:measuredbeamslices} (middle panel). At larger delays, especially near the negative delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models. The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then by the Airy beam. This is seen in the delay spectra for both baseline lengths, though the edge brightening is much clearer on the longer baseline where it less diluted by zero delay emission.

>>>>

\begin{figure*}[h]
\centering
\includegraphics[width=6in]{nithya_fg_pspec_all_lst.pdf}
\includegraphics[width=6in]{nithya_fg_pspec_lst0deg.pdf}
\includegraphics[width=6in]{nithya_fg_pspec_lst60deg.pdf}
\caption{Simulated foreground delay spectra using the HFSS beam at various LSTs (top panel). We plot the delay spectra at two LSTs spanning the range of possible horizon brightening for three different beam models. The maximum horizon brightening at the negative horizon occurs at 2$^\circ$ LST (middle panel), and the three beam models thus differ markedly in their predicted delay spectra near the horizon. In contrast, when the horizon brightening effect is smaller at 2$^\circ$ LST, the foreground delay spectra from all three beams agree much more closely.}
\label{fig:delayspec}
\end{figure*}

@@

NEED TO REVISE THIS PARAGRAPH FOR NITHYA'S SIMULATIONS, ALSO COMMENT ON THE CST-HFSS CURVE
How much do the predicted foreground power spectra differ between the three model dish power patterns? Figure \ref{fig:delayspec} (middle panel) shows the simulated delay spectra for all three beams at $2^\circ$ LST, when the horizon brightening is worst. All three delay spectra agree out to delays of 10--20\,ns on the 14\,m baseline and 30--40\,ns on the 40\,m baseline. These numbers suggest that the beams track each other fairly well out to 15--20$^\circ$ from zenith, beyond which they diverge. This is roughly what is observed in Figure \ref{fig:measuredbeamslices} (middle panel). At larger delays, especially near the negative delay horizon limit, all three model delay spectra diverge due to the significant edge brightening which effectively discriminates between these models. The CST, HFSS, and Airy beams reach roughly -35\,dB, -38\,dB, and -50\,dB at the horizon (Figure \ref{fig:modelbeams}), consistent with the fact that the CST beam has the largest horizon brightening, followed by the HFSS beam, and then by the Airy beam. This is seen in the delay spectra for both baseline lengths, though the edge brightening is much clearer on the longer baseline where it less diluted by zero delay emission.
